### 2023-09-02 sections/2-methods.tex
consistency of notation

We define a \emph{cluster} as a set of points with a \emph{center}, a \emph{radius}, and an approximation of the \emph{local fractal dimension}.
The \emph{center} is the geometric median of a sample of points in the \emph{cluster}, and so it is a real data point. The \emph{radius} is the
maximum distance from a point in the cluster to its \emph{center}. We estimate \emph{local fractal dimension} at the cluster radius and half
the cluster radius. Each cluster (unless it is a leaf cluster) has two child clusters in much the same way that a node in
a binary tree has two child nodes. We define the \emph{metric entropy} of a data set under a hierarchical clustering scheme as a refinement of [7], where
metric entropy for a given cluster radius $r_c$ was the number of clusters of radius $r_c$ needed to cover all data. Here, we use a hierarchical, divisive clustering 
approach, but with early stopping criteria; clusters which satisfy a user-specified stopping criterion (e.g. a specified cardinality or radius) are not further split. 
Since we frame the asymptotic complexity of $\rho$-NN search in terms of the number of leaf clusters, the \emph{metric entropy} is best thought of in terms of the number of
leaf clusters.

@@

In ~\cite{ishaq2019clustered}, we claimed that the complexity of coarse search for $\rho$-NN is $\mathcal{O}(\log{2}m)$, 
where $m$ is the metric entropy of the dataset. 
To adjust this bound for $k$-NN by Repeated $\rho$-NN, we must estimate the number of iterations 
of $\rho$-NN needed to find at least $k$ neighbors.

@@

Putting our bounds for coarse and fine search together, we have that $k$-NN by Repeated $\rho$-NN has 
$\mathcal{O}\left(\log_2{m} + k\left(\frac{r_i\left(\frac{k}{|C_i|}\right)^{\frac{1}{d_i}}+ 2r_c}{r_i\left(\frac{k}{|C_i|}\right)^{\frac{1}{d_i}}}\right)^d\right)$ 
time complexity, where $m$ is the metric entropy of the dataset, $d$ is the dimensionality of the dataset, $r_i$ is the radius of some cluster $C_i$
near the query ball, $d_i$ is the local fractal dimension of $C_i$, $r_c$ is the radius of leaf clusters, and $k$ is the number of nearest neighbors.

>>>>

We define a \emph{cluster} as a set of points with a \emph{center}, a \emph{radius}, and an approximation of the \emph{local fractal dimension}.
The \emph{center} is the geometric median of a sample of points in the \emph{cluster}, and so it is a real data point. The \emph{radius} is the
maximum distance from a point in the cluster to its \emph{center}. We estimate \emph{local fractal dimension} at the cluster radius and half
the cluster radius. Each cluster (unless it is a leaf cluster) has two child clusters in much the same way that a node in
a binary tree has two child nodes. We define the \emph{metric entropy} $\mathcal{N}_{\hat{r_c}}(D)$ of a data set $D$ under a hierarchical clustering scheme as a refinement of [7], where
metric entropy for a given cluster radius $r_c$ was the number of clusters of radius $r_c$ needed to cover all data. Here, we use a hierarchical, divisive clustering 
approach, but with early stopping criteria; clusters which satisfy a user-specified stopping criterion (e.g. a specified cardinality or radius) are not further split. 
Since we frame the asymptotic complexity of $\rho$-NN search in terms of the number of leaf clusters, the \emph{metric entropy} is best thought of in terms of the number of
leaf clusters.

@@

In ~\cite{ishaq2019clustered}, we claimed that the complexity of coarse search for $\rho$-NN is $\mathcal{O}(\log{2}$\mathcal{N}_{\hat{r_c}}(D)$)$, 
where $m$\mathcal{N}_{\hat{r_c}}(D)$$ is the metric entropy of the dataset $D$. 
To adjust this bound for $k$-NN by Repeated $\rho$-NN, we must estimate the number of iterations 
of $\rho$-NN needed to find at least $k$ neighbors.

@@

Putting our bounds for coarse and fine search together, we have that $k$-NN by Repeated $\rho$-NN has 
$\mathcal{O}\left(\log_2{\mathcal{N}_{\hat{r_c}}(D)} + k\left(\frac{r_i\left(\frac{k}{|C_i|}\right)^{\frac{1}{d_i}}+ 2r_c}{r_i\left(\frac{k}{|C_i|}\right)^{\frac{1}{d_i}}}\right)^d\right)$ 
time complexity, where $\mathcal{N}_{\hat{r_c}}(D) is the metric entropy of the dataset, $d$ is the dimensionality of the dataset, $r_i$ is the radius of some cluster $C_i$
near the query ball, $d_i$ is the local fractal dimension of $C_i$, $r_c$ is the radius of leaf clusters, and $k$ is the number of nearest neighbors.
